Quasars Probing Quasars IX. The Kinematics of the Circumgalactic Medium Surrounding $z\sim2$ Quasars

### 2018-02-28 QPQ9/Submit/qpq9_resubmit_3.tex
small changes

\begin{figure}
%\includegraphics[width=2.5in]{Figures/fig_monte.pdf}
\includegraphics[width=2.5in]{f05.pdf}
\caption{The same \ion{C}{2} mean stack shown in the first panel of
Figure~\ref{fig:stacks_and_fits} is shown in thin, black.
{\bf We overplot in dashed, yellow an
absorption profile with $\sigma_v=554\,{\rm km\,s^{-1}}$, which is larger than the observed width
by three times the standard deviation in the bootstrap analysis. Motions that produce a velocity
width larger than this can be ruled out. We overplot in dot dashed, yellow an absorption profile with
$\sigma_v=214\,{\rm km\,s^{-1}}$, which is smaller than the observed width by three times the
modeling error. Unless gravitational and Hubble flows together with redshift error broadening
produce a velocity width smaller than this, extra dynamical processes (e.g.\ outflows) will not be
required to explain the observed width.
In thick, gold, we overplot the
Gaussian absorption model of the Monte Carlo simulations generated from a purely clustering
argument. The model from clustering analysis is multiplied to the pseudo-continuum level of the
stack of the observational data, and broadened
by the mean redshift error in the data. While this model has a dispersion within modeling error of the
dispersion in the data. the centroid of the stack of the data appears to be redshifted
from the systemic. A model with only gravitational motions and Hubble flows cannot explain
this putative asymmetry.}
}
\label{fig:monte}
\end{figure}

>>>>

\begin{figure}
%\includegraphics[width=2.5in]{Figures/fig_monte.pdf}
\includegraphics[width=2.5in]{f05.pdf}
\caption{The same \ion{C}{2} mean stack shown in the first panel of
Figure~\ref{fig:stacks_and_fits} is shown in thin, black.
{\bf We overplot in dashed, limegreen an
absorption profile with $\sigma_v=554\,{\rm km\,s^{-1}}$, which is larger than the observed width
by three times the standard deviation in the bootstrap analysis. Motions that produce a velocity
width larger than this can be ruled out. We overplot in dot dashed, limegreen an absorption profile with
$\sigma_v=214\,{\rm km\,s^{-1}}$, which is smaller than the observed width by three times the
modeling error. Unless gravitational and Hubble flows together with redshift error broadening
produce a velocity width smaller than this, extra dynamical processes (e.g.\ outflows) will not be
required to explain the observed width.
In thick, green, we overplot the
Gaussian absorption model of the Monte Carlo simulations generated from a purely clustering
argument. The model from clustering analysis is multiplied to the pseudo-continuum level of the
stack of the observational data, and broadened
by the mean redshift error in the data. While this model has a dispersion within modeling error of the
dispersion in the data. the centroid of the stack of the data appears to be redshifted
from the systemic. A model with only gravitational motions and Hubble flows cannot explain
this putative asymmetry.}
}
\label{fig:monte}
\end{figure}
